### 2020-04-28 README.Rmd
Add get-db script

up = "https://github.com/cyipt/cyipt-bigdata/raw/master/osm-prep/Leeds/osm-lines.Rds"
roads = readRDS(url(up))
names(roads)
summary(roads$width)
wide_potential1 = roads %>% filter(width > 10, pct.dutch > 100)
mapview::mapview(wide_potential1)
wide_potential2 = roads %>% filter(lanes.forward > 1, pct.dutch > 100)
mapview::mapview(wide_potential2)
wide_potential3 = roads %>% filter(lanes.forward + lanes.backward > 2, pct.dutch > 100)
mapview::mapview(wide_potential3)

>>>>

up = "https://github.com/cyipt/cyipt-bigdata/raw/master/osm-prep/Leeds/osm-lines.Rds"
up = "https://github.com/cyipt/cyipt-bigdata/raw/master/osm-prep/Cambridge/osm-lines.Rds"
up = "https://github.com/cyipt/cyipt-bigdata/raw/master/osm-prep/Cambridge/osm-lines.Rds"
up = "https://github.com/cyipt/cyipt-bigdata/raw/master/osm-recc/Hereford/osm-lines.Rds"

roads = readRDS(url(up))
names(roads)
summary(roads$width)
wide_potential1 = roads %>% filter(width > 10, pct.dutch > 100)
mapview::mapview(wide_potential1)
wide_potential2 = roads %>% filter(
  lanes.forward > 1 |
  lanes.backward > 1,
  pct.dutch > 50)
mapview::mapview(wide_potential2)
wide_potential3 = roads %>% filter(lanes.forward + lanes.backward > 2, pct.dutch > 100)
mapview::mapview(wide_potential3)
